The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-09-02 floats/figures.tex
Merge latex2rtf and pdflatex main files
Add a copernicus_rtf input file and replace to-do notes by regular footnotes. Using a copernicus_rtf package or class file did not seem to work with latex2rtf.

% fig:locmap
\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=8cm]{cordillera-climate-locmap}
	\end{center}
    \irina[inline]{include all geographic names}
    \arjen[inline]{elevation scale white-end confused with glaciers}
    \arjen[inline]{remove Arctic circle and miles scale}
    \arjen[inline]{use CIS, LIS and IIS for ice sheet names}
    \arjen[inline]{use N, S, E and W instead of minus, add 75\degree N label}
	\caption{Shaded relief map of northern North America with the extent of the Cordilleran (CIS), Laurentide (LIS) and Innuitian (IIS) ice sheets at 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) \citep{dyke-2004}. The background map consists of ETOPO1 \citep{data:etopo1} and Natural Earth Data \citep{data:naturalearth}. Assembled with GRASS~GIS \citep{soft:grass} and Inkscape \citep{web:inkscape}}
	\label{fig:locmap}
\end{figure}

@@

% fig:ivolarea
\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=9cm]{cordillera-climate-ivolarea}
	\end{center}
	\julien[inline]{I will make the figure readable in black-and-white and highlight markers corresponding to the ``best'' runs.}
	\caption{Total ice volume and glaciated area after 10\,kyr as a function of temperature offset and climate forcing. Drawn using Matplotlib \citep{soft:mpl}.}
	\label{fig:ivolarea}
\end{figure}

>>>>

\emph{See to-do notes on Figure \ref{fig:locmap}
    \irina[inline]{include all geographic names}
    \arjen[inline]{elevation scale white-end confused with glaciers}
    \arjen[inline]{remove Arctic circle and miles scale}
    \arjen[inline]{use CIS, LIS and IIS for ice sheet names}
    \arjen[inline]{use N, S, E and W instead of minus, add 75\degree N label}
and \ref{fig:ivolarea}
    \julien[inline]{Make the figure print-proof and highlight markers corresponding to the ``best'' runs.}
}

% fig:locmap
\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=8cm]{cordillera-climate-locmap}
	\end{center}
	\caption{Shaded relief map of northern North America with the extent of the Cordilleran (CIS), Laurentide (LIS) and Innuitian (IIS) ice sheets at 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) \citep{dyke-2004}. The background map consists of ETOPO1 \citep{data:etopo1} and Natural Earth Data \citep{data:naturalearth}. Assembled with GRASS~GIS \citep{soft:grass} and Inkscape \citep{web:inkscape}}
	\label{fig:locmap}
\end{figure}

@@

% fig:ivolarea
\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=9cm]{cordillera-climate-ivolarea}
	\end{center}
	\caption{Total ice volume and glaciated area after 10\,kyr as a function of temperature offset and climate forcing. Drawn using Matplotlib \citep{soft:mpl}.}
	\label{fig:ivolarea}
\end{figure}
